Manuscript 4: Health Behaviors after the Crisis

### 2022-08-25 paperfour_healthbehaviors.Rmd
Updates in response to reviewer comments + tidying up

#mydata_complete$gender <- factor(mydata_complete$gender)
mydata_complete$reth <- factor(mydata_complete$reth)
mydata_complete$educ_level <- factor(mydata_complete$educ_level)
mydata_complete$employ_status <- factor(mydata_complete$employ_status)
mydata_complete$marital_status <- factor(mydata_complete$marital_status)
mydata_complete$current_housing <- factor(mydata_complete$current_housing)
mydata_complete$current_zip <- factor(mydata_complete$current_zip)
#mydata_complete$have_health_insurance <- factor(mydata_complete$have_health_insurance)
mydata_complete$access_vehicle <- factor(mydata_complete$access_vehicle)
mydata_complete$water_source <- factor(mydata_complete$water_source)
mydata_complete$water_test_event_ind <- factor(mydata_complete$water_test_event_ind)
mydata_complete$collapse_last_test <- factor(mydata_complete$collapse_last_test)
mydata_complete$get_free_bottled_water <- factor(mydata_complete$get_free_bottled_water)
mydata_complete$used_water_pod <- factor(mydata_complete$used_water_pod)
mydata_complete$waterline_replaced_eventind <- factor(mydata_complete$waterline_replaced_eventind)
mydata_complete$water_line_status_after_april2014 <- factor(mydata_complete$water_line_status_after_april2014)
mydata_complete$water_bottle_disposal <- factor(mydata_complete$water_bottle_disposal)
mydata_complete$bottled_water_other <- factor(mydata_complete$bottled_water_other)
mydata_complete$bottled_water_cleaning <- factor(mydata_complete$bottled_water_cleaning)
mydata_complete$bottled_water_teeth <- factor(mydata_complete$bottled_water_teeth)
mydata_complete$bottled_water_bathe <- factor(mydata_complete$bottled_water_bathe)
mydata_complete$bottled_water_cook <- factor(mydata_complete$bottled_water_cook)
mydata_complete$bottled_water_drink <- factor(mydata_complete$bottled_water_drink)
mydata_complete$current_water_source <- factor(mydata_complete$current_water_source)
mydata_complete$blood_test_before_april_2014 <- factor(mydata_complete$blood_test_before_april_2014)
mydata_complete$blood_test_after_april_2014 <- factor(mydata_complete$blood_test_after_april_2014)
mydata_complete$elevated_lead_before_april_2014 <- factor(mydata_complete$elevated_lead_before_april_2014)
mydata_complete$elevated_lead_after_april_2014 <- factor(mydata_complete$elevated_lead_after_april_2014)
mydata_complete$no_free_bottles_long_lines <- factor(mydata_complete$no_free_bottles_long_lines)
mydata_complete$no_free_bottles_bad_hours <- factor(mydata_complete$no_free_bottles_bad_hours)
mydata_complete$no_free_bottles_no_transport <- factor(mydata_complete$no_free_bottles_no_transport)
mydata_complete$no_free_bottles_too_far <- factor(mydata_complete$no_free_bottles_too_far)
mydata_complete$no_free_bottles_supply_limit <- factor(mydata_complete$no_free_bottles_supply_limit)
mydata_complete$no_free_bottles_dont_know <- factor(mydata_complete$no_free_bottles_dont_know)
mydata_complete$no_free_bottles_use_tap <- factor(mydata_complete$no_free_bottles_use_tap)
mydata_complete$no_free_bottles_other <- factor(mydata_complete$no_free_bottles_other)
mydata_complete$drink_tap_in_three_years <- factor(mydata_complete$drink_tap_in_three_years, levels = c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree"), ordered = TRUE)
mydata_complete$bottle_site <- factor(mydata_complete$bottle_site)

@@

number_water_tests <- with(imp_long_mids, lm(log(watertestnum + 0.1) ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2))

@@

## This model could not be fit because of small sample sizes.
#elev_blls <- with(imp_long_mids, glm(as.numeric(elevated_lead_after_april_2014=="Yes") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + water_source2 + number_children + confidants2, family = "binomial"))

#summary(pool(elev_blls))

#subdat <- data.frame("Outcome" = rep("Elevated BLLs", 18), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Other water source (ref: Flint tap water)", "Number of children", "Network size"), "Estimate" = summary(pool(elev_blls))$estimate[-1], "SE" = summary(pool(elev_blls))$std.error[-1], "Pval" = summary(pool(elev_blls))$p.value[-1])

#effect_estims <- rbind(effect_estims, subdat)

@@

number_bottles <- with(imp_long_mids, glm(num_bottles_per_day ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "quasipoisson"))

summary(pool(number_bottles))

subdat <- data.frame("Outcome" = rep("Number of bottles per day", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(number_bottles))$estimate[-1], "SE" = summary(pool(number_bottles))$std.error[-1], "Pval" = summary(pool(number_bottles))$p.value[-1])

@@

recycle_bottles <- with(imp_long_mids, glm(as.numeric(water_bottle_disposal=="I don't ever have plastic water bottles at home" | water_bottle_disposal=="Keep/save them for re-use or another purpose" | water_bottle_disposal=="Recycle them") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial"))

summary(pool(recycle_bottles))

subdat <- data.frame("Outcome" = rep("Bottle disposal", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(recycle_bottles))$estimate[-1], "SE" = summary(pool(recycle_bottles))$std.error[-1], "Pval" = summary(pool(recycle_bottles))$p.value[-1])

waterlinestatus <- with(imp_long_mids, glm(as.numeric(water_line_status_after_april2014=="A mailing or official said that my lead/water line did not need to be replaced" | water_line_status_after_april2014=="I was offered a lead/water line replacement but I refused it" | water_line_status_after_april2014=="My lead/water lines were replaced") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial"))

subdat <- data.frame("Outcome" = rep("Water line status", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(waterlinestatus))$estimate[-1], "SE" = summary(pool(waterlinestatus))$std.error[-1], "Pval" = summary(pool(waterlinestatus))$p.value[-1])

water_line_time <- with(imp_long_mids, coxph(Surv(water_line_surv, as.numeric(waterline_replaced_eventind)-1) ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2))

@@

subdat <- data.frame("Outcome" = rep("Time to water line replacement", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(water_line_time))$estimate, "SE" = summary(pool(water_line_time))$std.error, "Pval" = summary(pool(water_line_time))$p.value)

@@

#child_test <- with(imp_long_mids, glm(testpost2014_child ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + confidants2 + factor(blood_test_after_april_2014, ordered = FALSE) + offset(number_children), family = "quasipoisson"))

#summary(pool(child_test))

#subdat <- data.frame("Outcome" = rep("Got child tested", 23), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Network size", "Adult not tested (ref: Adult tested)", "Adult unsure if tested (ref: Adult tested)"), "Estimate" = summary(pool(child_test))$estimate[-1], "SE" = summary(pool(child_test))$std.error[-1], "Pval" = summary(pool(child_test))$p.value[-1])

#effect_estims <- rbind(effect_estims, subdat)

##This model not included because of stability issues:

#child_bll <- with(imp_long_mids, glm(bllpost2014_child ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + confidants2 + as.numeric(elevated_lead_after_april_2014=="Yes") + offset(number_children), family = "quasipoisson"))

#summary(pool(child_bll))

#subdat <- data.frame("Outcome" = rep("Child had elevated BLLs", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Network size", "Adult has elevated BLLs (ref: Adult has normal/unsure BLLs)"), "Estimate" = summary(pool(child_bll))$estimate[-1], "SE" = summary(pool(child_bll))$std.error[-1], "Pval" = summary(pool(child_bll))$p.value[-1])

#effect_estims <- rbind(effect_estims, subdat)

#child_bottled <- with(imp_long_mids, glm(bottledwater_child ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + confidants2 + factor(current_water_source2, ordered = FALSE) + offset(number_children), family = "quasipoisson"))

#summary(pool(child_bottled))

#subdat <- data.frame("Outcome" = rep("Child uses bottled water", 23), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Network size", "Adult uses filtered tap water (ref: Adult uses unfiltered water)", "Adult uses bottled water (ref: Adult uses unfiltered water)"), "Estimate" = summary(pool(child_bottled))$estimate[-1], "SE" = summary(pool(child_bottled))$std.error[-1], "Pval" = summary(pool(child_bottled))$p.value[-1])

#effect_estims <- rbind(effect_estims, subdat)
```

@@

```

>>>>

mydata_complete$reth <- factor(mydata_complete$reth)
mydata_complete$educ_level <- factor(mydata_complete$educ_level)
mydata_complete$employ_status <- factor(mydata_complete$employ_status)
mydata_complete$marital_status <- factor(mydata_complete$marital_status)
mydata_complete$current_housing <- factor(mydata_complete$current_housing)
mydata_complete$current_zip <- factor(mydata_complete$current_zip)
mydata_complete$access_vehicle <- factor(mydata_complete$access_vehicle)
mydata_complete$water_source <- factor(mydata_complete$water_source)
mydata_complete$water_test_event_ind <- factor(mydata_complete$water_test_event_ind)
mydata_complete$collapse_last_test <- factor(mydata_complete$collapse_last_test)
mydata_complete$get_free_bottled_water <- factor(mydata_complete$get_free_bottled_water)
mydata_complete$used_water_pod <- factor(mydata_complete$used_water_pod)
mydata_complete$waterline_replaced_eventind <- factor(mydata_complete$waterline_replaced_eventind)
mydata_complete$water_line_status_after_april2014 <- factor(mydata_complete$water_line_status_after_april2014)
mydata_complete$water_bottle_disposal <- factor(mydata_complete$water_bottle_disposal)
mydata_complete$bottled_water_other <- factor(mydata_complete$bottled_water_other)
mydata_complete$bottled_water_cleaning <- factor(mydata_complete$bottled_water_cleaning)
mydata_complete$bottled_water_teeth <- factor(mydata_complete$bottled_water_teeth)
mydata_complete$bottled_water_bathe <- factor(mydata_complete$bottled_water_bathe)
mydata_complete$bottled_water_cook <- factor(mydata_complete$bottled_water_cook)
mydata_complete$bottled_water_drink <- factor(mydata_complete$bottled_water_drink)
mydata_complete$current_water_source <- factor(mydata_complete$current_water_source)
mydata_complete$blood_test_before_april_2014 <- factor(mydata_complete$blood_test_before_april_2014)
mydata_complete$blood_test_after_april_2014 <- factor(mydata_complete$blood_test_after_april_2014)
mydata_complete$elevated_lead_before_april_2014 <- factor(mydata_complete$elevated_lead_before_april_2014)
mydata_complete$elevated_lead_after_april_2014 <- factor(mydata_complete$elevated_lead_after_april_2014)
mydata_complete$no_free_bottles_long_lines <- factor(mydata_complete$no_free_bottles_long_lines)
mydata_complete$no_free_bottles_bad_hours <- factor(mydata_complete$no_free_bottles_bad_hours)
mydata_complete$no_free_bottles_no_transport <- factor(mydata_complete$no_free_bottles_no_transport)
mydata_complete$no_free_bottles_too_far <- factor(mydata_complete$no_free_bottles_too_far)
mydata_complete$no_free_bottles_supply_limit <- factor(mydata_complete$no_free_bottles_supply_limit)
mydata_complete$no_free_bottles_dont_know <- factor(mydata_complete$no_free_bottles_dont_know)
mydata_complete$no_free_bottles_use_tap <- factor(mydata_complete$no_free_bottles_use_tap)
mydata_complete$no_free_bottles_other <- factor(mydata_complete$no_free_bottles_other)
mydata_complete$drink_tap_in_three_years <- factor(mydata_complete$drink_tap_in_three_years, levels = c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree"), ordered = TRUE)
mydata_complete$bottle_site <- factor(mydata_complete$bottle_site)

@@

number_water_tests <- with(imp_long_mids, glm(watertestnum ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "poisson"))

@@

@@

waterlinestatus <- with(filter(imp_long_mids, water_source2=="Tap water through the City of Flint"), glm(as.numeric(water_line_status_after_april2014=="A mailing or official said that my lead/water line did not need to be replaced" | water_line_status_after_april2014=="I was offered a lead/water line replacement but I refused it" | water_line_status_after_april2014=="My lead/water lines were replaced") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + number_children + confidants2, family = "binomial"))

subdat <- data.frame("Outcome" = rep("Water line status", 21), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(waterlinestatus))$estimate[-1], "SE" = summary(pool(waterlinestatus))$std.error[-1], "Pval" = summary(pool(waterlinestatus))$p.value[-1])

@@

water_line_time <- with(filter(imp_long_mids, water_source2=="Tap water through the City of Flint"), coxph(Surv(water_line_surv, as.numeric(waterline_replaced_eventind)-1) ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + number_children + confidants2))

@@

subdat <- data.frame("Outcome" = rep("Time to water line replacement", 21), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(pool(water_line_time))$estimate, "SE" = summary(pool(water_line_time))$std.error, "Pval" = summary(pool(water_line_time))$p.value)

@@

effect_estims <- rbind(effect_estims, subdat)
```

@@

At reviewer request, we redo the above modeling using only the complete data, without multiple imputation:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
mydata_complete$zip2 <- case_when(
  mydata_complete$current_zip=="48502" | mydata_complete$current_zip=="48503" ~ "48502/48503",
  mydata_complete$current_zip=="48504" ~ "48504",
  mydata_complete$current_zip=="48505" ~ "48505",
  mydata_complete$current_zip=="48506" ~ "48506",
  mydata_complete$current_zip=="48507" | mydata_complete$current_zip=="48532" ~ "48507/48532"
)

mydata_complete$educ_level2 <- case_when(
  mydata_complete$educ_level=="Less than a high school diploma" | mydata_complete$educ_level=="High school degree or equivalent (e.g. GED)" ~ "High school or less",
  mydata_complete$educ_level=="Some college, no degree" ~ "Some college",
  mydata_complete$educ_level=="Associate degree" | mydata_complete$educ_level=="Bachelor's degree" | mydata_complete$educ_level=="Master's, Doctoral or Professional degree" ~ "Associate's or more"
)

mydata_complete$public_benefits2 <- ifelse(mydata_complete$public_benefits=="Yes", "Yes", "No")
mydata_complete$gender2 <- ifelse(mydata_complete$gender=="Transgender Woman", "Female", mydata_complete$gender)

mydata_complete$marital_status2 <- case_when(
  mydata_complete$marital_status=="Single (never married)" ~ "Single (never married)",
  mydata_complete$marital_status=="Married" ~ "Married", 
  mydata_complete$marital_status=="Separated" | mydata_complete$marital_status=="Divorced" | mydata_complete$marital_status=="Widowed" ~ "Separated"
)

mydata_complete$employ_status2 <- case_when(
  mydata_complete$employ_status=="Jobs/sporadic" | mydata_complete$employ_status=="Other" ~ "Other",
  mydata_complete$employ_status=="Retired" ~ "Retired",
  mydata_complete$employ_status=="Employed" ~ "Employed",
  mydata_complete$employ_status=="Unemployed" ~ "Unemployed",
  is.na(mydata_complete$employ_status) ~ NA_character_)

mydata_complete$reth2 <- case_when(
  mydata_complete$reth=="Black" ~ "Black",
  mydata_complete$reth=="White" ~ "White",
  mydata_complete$reth=="Mixed Race" | mydata_complete$reth=="American Indian" | mydata_complete$reth=="Other race" | mydata_complete$reth=="Asian" | mydata_complete$reth=="Hispanic/Latinx" ~ "Other"
)

mydata_complete$current_housing2 <- case_when(
  mydata_complete$current_housing=="You own a home" ~ "Owned home",
  mydata_complete$current_housing=="You rent a home" ~ "Rented home",
  mydata_complete$current_housing=="You are staying with family or a friend" | mydata_complete$current_housing=="You are at a shelter" | mydata_complete$current_housing=="You are crashing/couch-surfing somewhere" | mydata_complete$current_housing=="You are on the streets" ~ "Unstable housing",
  mydata_complete$current_housing=="You are at a retirement facility" | mydata_complete$current_housing=="You are in an in-patient setting (e.g., rehab)" | mydata_complete$current_housing=="Other" ~ "Other housing"
)

mydata_complete$have_health_insurance2 <- ifelse(mydata_complete$have_health_insurance=="Unsure/Don't know", "No", mydata_complete$have_health_insurance)

mydata_complete$water_source2 <- ifelse(mydata_complete$water_source=="Tap water through the City of Flint (Water Department etc.)", "Tap water through the City of Flint", "Other")

mydata_complete$current_water_source2 <- case_when(
  mydata_complete$current_water_source=="Bottled water" | mydata_complete$current_water_source=="I don't drink any water at home" ~ "Bottled water",
  mydata_complete$current_water_source=="Tap water (with a filter)" | mydata_complete$current_water_source=="Water from a filtration system" ~ "Filtered tap water",
  mydata_complete$current_water_source=="Tap water (without a filter)" ~ "Unfiltered tap water"
)

mydata_complete$zip2 <- factor(mydata_complete$zip2)
mydata_complete$educ_level2 <- factor(mydata_complete$educ_level2, levels = c("High school or less", "Some college", "Associate's or more"))
mydata_complete$public_benefits2 <- factor(mydata_complete$public_benefits2)
mydata_complete$marital_status2 <- factor(mydata_complete$marital_status2)
mydata_complete$employ_status2 <- factor(mydata_complete$employ_status2)
mydata_complete$reth2 <- factor(mydata_complete$reth2)
mydata_complete$current_housing2 <- factor(mydata_complete$current_housing2, levels = c("Owned home", "Rented home", "Unstable housing", "Other housing"))
mydata_complete$have_health_insurance2 <- factor(mydata_complete$have_health_insurance2)
mydata_complete$water_source2 <- factor(mydata_complete$water_source2, levels = c("Tap water through the City of Flint", "Other"))
mydata_complete$current_water_source2 <- factor(mydata_complete$current_water_source2, levels = c("Unfiltered tap water", "Filtered tap water", "Bottled water"), ordered = TRUE)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
effect_estims <- data.frame("Outcome" = NA, "Predictor" = NA, "Estimate" = NA, "SE" = NA, "Pval" = NA)

time_to_notice <- lm(log(num_time_notice) ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + water_source2 + access_vehicle + number_children + confidants2, data = mydata_complete)

summary(time_to_notice)

subdat <- data.frame("Outcome" = rep("Time to notice", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(time_to_notice)$coefficients[-1, 1], "SE" = summary(time_to_notice)$coefficients[-1, 2], "Pval" = summary(time_to_notice)$coefficients[-1, 4])

number_water_tests <- glm(watertestnum ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, data = mydata_complete, family = "poisson")

summary(number_water_tests)

subdat <- data.frame("Outcome" = rep("Number of water tests", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(number_water_tests)$coefficients[-1,1], "SE" = summary(number_water_tests)$coefficients[-1,2], "Pval" = summary(number_water_tests)$coefficients[-1,4])

last_water_test_time <- coxph(Surv(water_test_surv, as.numeric(water_test_event_ind)-1) ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, data = mydata_complete)

summary(last_water_test_time)

subdat <- data.frame("Outcome" = rep("Time to last water test", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(last_water_test_time)$coefficients[,1], "SE" = summary(last_water_test_time)$coefficients[,3], "Pval" = summary(last_water_test_time)$coefficients[,5])

last_test_result <- glm(as.numeric(collapse_last_test=="Acceptable levels of lead") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial", data = mydata_complete)

summary(last_test_result)

subdat <- data.frame("Outcome" = rep("Last water test result", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(last_test_result)$coefficients[-1,1], "SE" = summary(last_test_result)$coefficients[-1,2], "Pval" = summary(last_test_result)$coefficients[-1,4])

blood_test <- glm(as.numeric(blood_test_after_april_2014=="Yes") ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial", data = mydata_complete)

summary(blood_test)

subdat <- data.frame("Outcome" = rep("Blood test", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(blood_test)$coefficients[-1, 1], "SE" = summary(blood_test)$coefficients[-1, 2], "Pval" = summary(blood_test)$coefficients[-1, 4])

currentwatersource <- polr(current_water_source2 ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, Hess = TRUE, data = mydata_complete)

summary(currentwatersource)

subdat <- data.frame("Outcome" = rep("Current drinking water source", 22), "Predictor" = c("Age", "Other race (ref: Black race)", "White race (ref: Black race)", "Male (ref: Female)", "Some college (ref: High school or less)", "Associate's degree or more (ref: High school or less", "Separated (ref: Married)", "Single (ref: Married)", "No public benefits (ref: Receives public benefits)", "Unsure if receives public benefits (ref: Receives public benefits)", "Health insured (ref: Uninsured)", "Other employment (ref: Employed)", "Retired (ref: Employed)", "Unemployed (ref: Employed)", "Years lived in Flint", "Rented home (ref: Owned home)", "Unstable housing (ref: Owned home)", "Other housing (ref: Owned home)", "Other water source (ref: Flint tap water)", "Has vehicle (ref: No vehicle)", "Number of children", "Network size"), "Estimate" = summary(currentwatersource)$coefficients[1:22,1], "SE" = summary(currentwatersource)$coefficients[1:22,2], "Pval" = NA)

water_pod_past <- glm(used_water_pod ~ age + reth2 + gender2 + educ_level2 + marital_status2 + public_benefits + have_health_insurance2 + employ_status2 + years_cityflint + current_housing2 + access_vehicle + water_source2 + number_children + confidants2, family = "binomial", data = mydata_complete)

summary(water_pod_past)
